An efficient composition of bidirectional programs by tupling and lazy updates

### 2020-02-21 paper/5.experiments.tex
Tiny update
Polished English of last paragraph.

We have fully implemented and tested all methods% 
%
\footnote{All experiments on macOS 10.14.6, processor Intel Core i7 (2.6~GHz), RAM 16~GB 2400~MHz DDR4, OCaml 4.07.1. The OCaml runtime system options and garbage collection parameters are set as default.}$^,$%HACK!
%
\footnote{Anonymous \url{https://mega.nz/\#F!ec8y2ITa!tLOHKkHgs_7fjSI8m-O26Q}}
%
described in the previous sections. Our target language is untyped. Some dummies used for $pg$, $cpg$, $kpg$ and $xpg$ are replaced with the current updated views. This helps a program in the $put$ direction valid.

@@

\textcolor{red}{TODO-D4: emphasize overhead of memoization. it is not for free.}
Figure \ref{fig:result} 
% illustrates 
shows the evaluation times for each of the seven test cases using the three methods: $put$ in minBiGUL, $put_m$ in minBiGUL$_m$ and $xpg$.
We also did similar experiments with $pg$, $cpg$ and $kpg$, but their results are slower than the corresponding ones of $xpg$. The slowness was caused by the exponential number of $pg$ calls in the case of $pg$, redundant evaluations ($cpg$), and redundant overhead for constructing closures ($kpg$).
Therefore we simply omit these results in Figure \ref{fig:result}.
As we all know, $put$ works poorly for left associative compositions because of the number of reevaluated $get$s.
%The figure shows $put_m$ and $xpg$ are better than $put$ in some cases.
The left part of the figure contains tests using not-large inputs, and we see that $put_m$ is the fastest method for them. However if the input size is large enough, in the cases of the right part of the figure, $put_m$ will be slower quickly due to time for manipulating data in the table. At that time, $xpg$ is 
% proved to be
the most effective method.
\textcolor{red}{TODO-B2: add short evaluation result of memory.}

>>>>

We have fully implemented and tested all methods% 
%
\footnote{All experiments on macOS 10.14.6, processor Intel Core i7 (2.6~GHz), RAM 16~GB 2400~MHz DDR4, OCaml 4.07.1. The OCaml runtime system options and garbage collection parameters are set as default.}$^,$%HACK!
%
\footnote{\textcolor{red}{The implementation is available:} \url{https://github.com/k-tsushima/pgs}}
%
described in the previous sections. Our target language is untyped. Some dummies used for $pg$, $cpg$, $kpg$ and $xpg$ are replaced with the current updated views. This helps a program in the $put$ direction valid.

@@

Figure \ref{fig:result} 
% illustrates 
shows the evaluation times for each of the seven test cases using the three methods: $put$ in minBiGUL, $put_m$ in minBiGUL$_m$ and $xpg$.
We also did similar experiments with $pg$, $cpg$ and $kpg$, but their results are slower than the corresponding ones of $xpg$. The slowness was caused by the exponential number of $pg$ calls in the case of $pg$, redundant evaluations ($cpg$), and redundant overhead for constructing closures ($kpg$).
Therefore we simply omit these results in Figure \ref{fig:result}.
As we all know, $put$ works poorly for left associative compositions because of the number of reevaluated $get$s.
%The figure shows $put_m$ and $xpg$ are better than $put$ in some cases.
The left part of the figure contains tests using not-large inputs, and we see that $put_m$ is the fastest method for them. However if the input size is large enough, in the cases of the right part of the figure, $put_m$ will be slower quickly due to time for manipulating data in the table. At that time, $xpg$ is 
% proved to be
the most effective method.

\textcolor{red}{Note that this result concerns BX programs that uses many compositions. If the number of compositions is small, $put$ will be fastest because of the overhead for memoization ($put_m$) and the overhead for keeping complements in closures ($xpg$).}

%\textcolor{red}{TODO-B2: add short evaluation result of memory.}
